---
title: "burnSummaries Manual"
subtitle: "v.`r SpaDES.core::moduleMetadata(module = 'burnSummaries', path = '..')$version`"
date: "Last updated: `r Sys.Date()`"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: sandstone
    number_sections: false
    df_print: paged
    keep_md: yes
editor_options:
  chunk_output_type: console
  markdown: 
    wrap: 80
bibliography: citations/references_burnSummaries.bib
citation-style: citations/ecology-letters.csl
link-citations: true
always_allow_html: true
---

# burnSummaries Module

<!-- the following are text references used in captions for LaTeX compatibility -->
(ref:burnSummaries) *burnSummaries*

(ref:percent) %

```{r setup-burnSummaries, include=FALSE}
## set cache.rebuild = TRUE whenever there are changes to the module code/metadata
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, warning = FALSE, 
                      cache = TRUE, cache.rebuild = FALSE, results = "hold", dpi = 300)

## get citation style
if (!file.exists("citations/ecology-letters.csl")) {
  dir.create("citations", showWarnings = FALSE)
  download.file("https://www.zotero.org/styles/ecology-letters?source=1", destfile = "citations/ecology-letters.csl")
}

library(Require)

Require(c("SpaDES.core", "git2r", "dplyr", "data.table", "kableExtra",
          "pander", "PredictiveEcology/SpaDES.docs"),
        upgrade = FALSE, install = FALSE)

```

```{r badgeFigs-burnSummaries, include = FALSE, eval = TRUE, cache = FALSE}
dir.create("figures", showWarnings = FALSE)

if (!file.exists("figures/markdownBadge.png")) {
  download.file(url = "https://img.shields.io/badge/Made%20with-Markdown-1f425f.png",
                destfile = "figures/markdownBadge.png",
                mode = "wb")
}
if (!file.exists("figures/issuesBadge.png")) {
  download.file(url = "https://img.shields.io/badge/Get%20help-Report%20issues-%3CCOLOR%3E.png",
                destfile = "figures/issuesBadge.png",
                mode = "wb")
}

modversion <- paste(unlist(moduleMetadata(module = 'burnSummaries', path = '..')$version), collapse = ".")
download.file(url = paste0("https://img.shields.io/badge/burnSummaries-", paste0("v.%20", modversion),
                           "-%3CCOLOR%3E.png"),
              destfile = "figures/moduleVersionBadge.png",
              mode = "wb")
```

``` {r moduleBadge-burnSummaries, echo = FALSE, eval = TRUE, cache = FALSE, results = "asis"}
## try to automatically get the commit URL and the path to the badge image
modulePath <- if (grepl("burnSummaries$", normPath("."))) {
    normPath(".")
  } else {
    modulePath <- grep("burnSummaries$", 
                       list.files(pattern = "burnSummaries", recursive = TRUE, include.dirs = TRUE),
                       value = TRUE)
    modulePath <- grep("docs/", modulePath, value = TRUE, invert = TRUE)  ## exclude "copied" modules dirs for bookdown
    normPath(modulePath)
  }

badgeURL <- if (!is_detached(modulePath)) {
  commitSHA <- sha(revparse_single(modulePath, "HEAD"))
  repo <- sub("[.]git$", "/commit/",
              branch_remote_url(branch_get_upstream(repository_head(modulePath))))
  paste0(repo, commitSHA)
} else {
  ## if detached point to the first remote
  remote_url(modulePath)[1]
}
badgeURL <- sub(".*github[.]com:", "https://github.com/", badgeURL)

badgePath <- normPath("figures/moduleVersionBadge.png")

## make string of markdown code to be executed as-is
cat(paste0("[![module-version-Badge](", badgePath, ")](", badgeURL, ")"))
```

```{r issuesBadge-burnSummaries, echo = FALSE, eval = TRUE, cache = FALSE, results = "asis"}
badgeURL <- "https://github.com/PredictiveEcology/burnSummaries/issues"
badgePath <- normPath("figures/issuesBadge.png")

## make string of markdown code to be executed as-is
cat(paste0("[![Issues-badge](", badgePath, ")](", badgeURL,")"))
```

#### Authors:

`r paste(as.character(SpaDES.core::moduleMetadata(module = "burnSummaries", path = '..')$authors), sep = ', ')`
<!-- ideally separate authors with new lines, '\n' not working -->

:::{.rmdwarning}
This documentation is work in progress.
Please report any discrepancies or omissions at <https://github.com/PredictiveEcology/BC_HRV_preamble/issues>.
:::

## Module Overview

### Module summary

(TODO)

- LandMine [@Andison:1996] - based on [@Clarke:1994];
- scfm [@Cumming:1998; @Armstrong:2003];
- fireSense [@Marchal:2017a; @Marchal:2017b; @Marchal:2019]

### Module inputs and parameters

Table \@ref(tab:moduleInputs-burnSummaries) shows the full list of module inputs.

```{r moduleInputs-burnSummaries, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
df_inputs <- SpaDES.core::moduleInputs("burnSummaries", "..")
knitr::kable(df_inputs,
             caption = "List of (ref:burnSummaries) input objects and their description.") |>
  kableExtra::kable_styling(latex_options = "scale_down", full_width = FALSE)
```

Provide a summary of user-visible parameters (Table \@ref(tab:moduleParams-burnSummaries))


```{r moduleParams-burnSummaries, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
df_params <- SpaDES.core::moduleParams("burnSummaries", "..")
knitr::kable(df_params, caption = "List of (ref:burnSummaries) parameters and their description.") |>
  kableExtra::kable_styling(latex_options = "scale_down", full_width = FALSE)
```

### Events

Describe what happens for each event type.

### Plotting

Write what is plotted.

### Saving

Write what is saved.

### Module outputs

Description of the module outputs (Table \@ref(tab:moduleOutputs-burnSummaries)).

```{r moduleOutputs-burnSummaries, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
df_outputs <- SpaDES.core::moduleOutputs("burnSummaries", "..")
knitr::kable(df_outputs, caption = "List of (ref:burnSummaries) outputs and their description.") |>
  kableExtra::kable_styling(latex_options = "scale_down", full_width = FALSE)
```

### Links to other modules

Describe any anticipated linkages to other modules, such as modules that supply input data or do post-hoc analysis.

### Getting help

- <https://github.com/PredictiveEcology/burnSummaries/issues>

### References

<!-- autogenerated -->
